---
title       : Developing Data Products
subtitle    : MPG Lienar Regression
author      : Marcelo Gomes Marques
date        : Monday, June 23, 2014
output      : ioslides_presentation
framework   : html5slides   # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : bootstrap     # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}

---

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

